Constraints on Assembly Bias from Galaxy Clustering

### 2016-05-25 ms.tex
Added information on priors, some text.

@@

Prior to discussing our results using models that include assembly bias, we present 
results of standard HOD analyses that include no model for assembly bias.

@@

>>>>

%---------------------------
\subsection{Halotools Implementation of HOD Models}
\label{subsection:halotools}
%---------------------------

%---------------------------
\subsection{HOD with Assembly Bias: The Decorated HOD}
\label{subsection:decorated}
%---------------------------

%---------------------------
\subsection{Parameter Inference}
\label{subsection:mcmc}
%---------------------------

To infer parameters for the HOD and Decorated HOD models described in the previous subsections, 
we performed a Markov Chain Monte Carlo (MCMC) sampling of the posteriors using the 
affine-invariant ensemble sampler of \citet{goodman_weare10} as implemented in the 
{\tt emcee} software package \citep{foreman-mackey_etal13}. For most cases, we find that 
$\sim 3-10 \times 10^{6}$ samples are necessary in order for our chains to converge.

%-------------------------------------------------------------------------------------------------------------------------------------------------
\begin{table}
\begin{center}
{\renewcommand{\arraystretch}{1.3}
\renewcommand{\tabcolsep}{0.2cm}
\begin{tabular}{l c}
\hline 
\hline
Parameter & Prior Interval\\ 
\hline
$\log (M_{\mathrm{min}})$ & [9.0,14.0] \\
$\sigma_{\log M}$ & [0.01,1.5] \\
$\log (M_0)$ & [9.0,14.0]\\
$\log (M_1)$ & [10.7,15.0]\\
$\alpha$ & [0.0,2.0]\\
$A_{\mathrm{cen}}$ & [-1.0,1.0]\\
$A_{\mathrm{sat}}$ & [-1.0,1.0]\\
\hline
\end{tabular}
\medskip
\caption{
Ranges for the priors used in the parameter inference. All prior distributions are uniform over the 
specified ranges.}
 }
 \label{table:priors}
 \end{center}
\end{table}
%--------------------------------------------------------------------------------------------------------------------------------

The most important detail of this analysis is the priors on the parameters. In all analyses 
discussed in this paper, we adopt priors that are uniform distributions over the intervals 
specified in Table~\ref{table:priors}. In the case of the assembly bias parameters 
$A_{\mathrm{cen}}$ and $A_{\mathrm{sat}}$, the priors represent physical 
boundaries. These parameters must satisfy $-1 \le A_{\mathrm{cen,sat}} \le 1$. 
Physical considerations require parameter $\sigma_{\log M} > 0$. All other 
priors have a negligible influence on the posterior aside from $\log M_0$. 
We find that $\log M_0$ is often very poorly constrained by clustering data.

@@

Prior to discussing our results using models that include assembly bias, we present 
results of standard HOD analyses that include no model for assembly bias. The results of 
the standard HOD analyses and all other analyses are shown in the form of marginalized 
constraints on individual parameters in Table~\ref{table:parameters}. We compare our parameter 
constraints to the standard HOD analysis performed by \citet{zehavi_etal11} in Table~\ref{table:parameters} 
as well.

@@

\bibliography{ms.bib}
